---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# donothing

<!-- badges: start -->
<!-- badges: end -->

The aim of this is to saving the annoyance of commenting a pipe ``%>%``.

## Installation

You can install the development version from [GitHub](https://github.com/alejandroxag) with:

``` {r warnings=FALSE,message=FALSE}
# install.packages("devtools")
devtools::install_github("alejandroxag/donothing")
library(donothing)
```

## Example

When working with a series of instructions piped down together, it's straightforward to comment any of them, except the last one, since the previous pipe is left pointing nowhere. ``donothing()`` is intended to be that last line that won't be commented.

Easier to do this

```{r}
t <- tibble::tibble(x = 1:2) %>% 
    dplyr::mutate(y = letters[1:2]) %>%
    # dplyr::mutate(y = LETTERS[1:7]) %>%
    donothing::donothing()
t
```

rather than this

```{r}
t <- tibble::tibble(x = 1:2) %>% 
    dplyr::mutate(y = letters[1:2]) #%>% 
    # dplyr::mutate(y = letters[1:7])
t
```

